---
title: "turk_results"
author: "Gurdit Chahal, Adam Letcher, Carlos Castro, Noah Randolph"
date: "8/7/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(stargazer)
library(pwr)
library(ggplot2)
library(sandwich)
library(AER)
```

## Load Data

```{r load}
dt_raw <- fread('musicdata.8.11.2018.csv')

head(dt_raw)
```

## Clean Up Columns

```{r}
dt <- dt_raw[, .(hear_song = as.integer(as.character(factor(Check1, levels = c('A', 'B'),
                                                            labels = c(1, 0)))), 
                 piano_playing = as.integer(as.character(factor(Check2, 
                                                                levels = c('A', 'B'), 
                                                                labels = c(1, 0)))),
                 q1 = as.factor(Q1), 
                 q2 = as.factor(Q2), 
                 q3 = as.factor(Q3),
                 q4 = as.factor(Q4),
                 q5 = as.factor(Q5),
                 age = factor(Q6, levels = c('A', 'B', 'C', 'D', 'E',
                                             'F', 'G', 'H', 'I', 'J'),
                              labels = c('<12', '12-17', '18-24', '25-34', '35-44',
                                         '45-54', '55-64', '65-74', '>75', 'decline')),
                 gender = factor(Q7, levels = c('A', 'B', 'C', 'D'), 
                                 labels = c('male', 'female', 'other', 'decline')),
                 own_dog = as.integer(as.character(factor(Q8, levels = c('A', 'B'), 
                                                          labels = c(1, 0)))),
                 education = factor(Q9, levels = c('A', 'B', 'C', 'D', 'E', 
                                                   'F', 'G', 'H', 'I', 'J'), 
                                    labels = c('none', '8th grade', 'some high school',
                                               'high school completed', 'some college', 
                                               'vocational', 'associates', 'bachelors', 
                                               'masters', 'doctorate')),
                 occupation = Q10, 
                 native_english = as.integer(as.character(factor(Q11, 
                                                                 levels = c('A', 'B'), 
                                                                 labels = c(1, 0)))), 
                 heard_lyrics = factor(Q13, levels = c('A', 'B', 'C', 'D', 'E', 'F'),
                                                               labels = c('I\'m a barbie girl', 
                                                                          'Rocket Man', 
                                                                          'Don\'t stop believing',
                                                                          'Hakuna Matata',
                                                                          'Lyrics but not sure',
                                                                          'No lyrics')),
                 is_turk = as.integer(as.character(factor(isTurk, 
                                                          levels = c('true', 'null'),
                                                          labels = c(1, 0)))),
                 time = time * -1, 
                 correct_count = correctCount, 
                 assigned_lyrics = as.numeric(lyrics),
                 lyrics_factor = factor(lyrics))]
```


## EDA

```{r}
summary(dt)
```


```{r, results='asis'}
stargazer(dt, header=FALSE,type='text')
```



Gender counts of treatment and control:
```{r}
dt[, .N, by = 'assigned_lyrics,gender']

ggplot(data = dt, aes(x = gender, group = lyrics_factor, fill = lyrics_factor)) + 
  geom_bar() + 
  theme_bw() +
  guides(fill=guide_legend(title="assignment")) +
  labs(
    title = "Treatment Assignment by Gender",
    x = "gender",
    y = "count"
    )
ggsave("gender_treatment_assignment.png")
```


Most people recognized the song regardless of being assigned lyrics:
```{r}
dt[, .N, by = 'heard_lyrics,assigned_lyrics']
```

Turkers took roughly 40% less time to complete the survey than non-turkers:
```{r}
dt[, mean(time), by = 'is_turk']

dt[ , t.test(time ~ is_turk)]
```


No significant difference in time taken based on treatment vs. control assignment:
```{r}
dt[, mean(time), by = 'assigned_lyrics']

dt[ , t.test(time ~ assigned_lyrics)]
```


## Covariate Balance Check

```{r}
table(dt$assigned_lyrics, dt$age)
```


```{r}
# assignment_by_age <- table(dt$assigned_lyrics, dt$age)
# barplot(assignment_by_age, main = 'Treatment Assignment by Age',
#         xlab = "Age Range", col = c('darkblue', 'red'),
#         legend = c('no lyrics', 'lyrics'))

# dt[, .N, keyby = 'age,assigned_lyrics']

ggplot(data = dt, aes(x = age, group = lyrics_factor, fill = lyrics_factor)) + 
  geom_bar() + 
  theme_bw() +
  guides(fill=guide_legend(title="assignment")) +
  labs(
    title = "Treatment Assignment by Age",
    x = "age range",
    y = "count"
    )
ggsave("treatment_by_age.png")
```

```{r}
table(dt$assigned_lyrics, dt$education)
```


```{r}
ggplot(data = dt, aes(x = education, group = lyrics_factor, fill = lyrics_factor)) + 
  geom_bar() + 
  theme_bw() +
  guides(fill=guide_legend(title="assignment")) +
  labs(
    title = "Treatment Assignment by Education",
    x = "education level",
    y = "count"
    ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))
ggsave("treatment_by_education.png")
```





```{r}
dt[ , chisq.test(assigned_lyrics, age, simulate.p.value = TRUE)]
dt[ , chisq.test(assigned_lyrics, education, simulate.p.value = TRUE)]
dt[,chisq.test(assigned_lyrics,gender,simulate.p.value = TRUE)]
dt[ , t.test(native_english ~ assigned_lyrics)]
dt[ , t.test(is_turk ~ assigned_lyrics)]
dt[ , t.test(own_dog ~ assigned_lyrics)]
dt[ , t.test(native_english ~ assigned_lyrics)]

```


## Results
```{r}
# correct_count_by_assignment <- table(dt$assigned_lyrics, dt$correct_count)
# x <- barplot(correct_count_by_assignment, main = 'Correct Count by Treatment Assignment',
#         col = c('orange', 'purple'), beside = TRUE, space = c(0, 0.2),
#         legend = c('no lyrics', 'lyrics'), args.legend = c(xjust = 5))

# ggplot(data = dt, aes(x = correct_count, group = lyrics_factor, fill = lyrics_factor)) + 
#   geom_bar(position = "dodge") + 
#   theme_bw() +
#   guides(fill=guide_legend(title="assignment")) +
#   labs(
#     title = "Correct Answers by Treatment Assignment",
#     x = "number of correct answers",
#     y = "count"
#     )

ggplot(data = dt, aes(x = lyrics_factor, y = correct_count, 
                      group = lyrics_factor, fill = lyrics_factor)) + 
  geom_jitter(width = .05, alpha = .4) +
  stat_summary(fun.data="mean_sdl", colour = 'red', size = .75, fun.args = 1) +
  guides(fill = "none") +
    theme_bw() +
    labs(
      title = "Correct Answer Distributions",
      x = "treatment assignment",
      y = "number of correct answers"
    )
ggsave("answers_individual_values.png", width = 3)
```


```{r}
# ggplot(data = dt, aes(x = lyrics_factor, y = time, group = lyrics_factor, fill = lyrics_factor)) + 
#   geom_boxplot(alpha = .7, varwidth = TRUE) + 
#   geom_jitter(width = .05, alpha = .4) +
#   guides(fill = "none") +
#     theme_bw() +
#     labs(
#       title = "Time Distributions Under Treatment and Control",
#       x = "treatment assignment",
#       y = "seconds to complete quiz/survey"
#     )
# ggsave("time_individual_values.png")

ggplot(data = dt, aes(x = lyrics_factor, y = time, 
                      group = lyrics_factor, fill = lyrics_factor)) + 
  geom_jitter(width = .05, alpha = .4) +
  stat_summary(fun.data="mean_sdl", colour = 'red', size = .75, fun.args = 1) +
  guides(fill = "none") +
    theme_bw() +
    labs(
      title = "Time Distributions",
      x = "treatment assignment",
      y = "seconds to complete quiz/survey"
    )
ggsave("time_individual_values.png", width = 3)
```


## Regression


No significant difference in scores between treatment and control groups:
```{r}
fit_simple <- lm(correct_count ~ assigned_lyrics, dt)
cov_simple <- vcovHC(fit_simple, type = 'HC')
robust.se_simple <- sqrt(diag(cov_simple))
```

With covariates
```{r}
fit_with_covariates <- lm(correct_count ~ assigned_lyrics + gender + native_english + own_dog + is_turk, dt)
cov_with_covariates <- vcovHC(fit_with_covariates, type = 'HC')
robust.se_with_covariates <- sqrt(diag(cov_with_covariates))
```


```{r, results='asis'}
stargazer(fit_simple, fit_with_covariates, 
          se=list(robust.se_simple, robust.se_with_covariates),
          dep.var.labels=c("correct answer count"),
          covariate.labels=c("assigned lyrics","female", "native english speaker","owns dog","mechanical turk"),
          keep.stat="n",type='text')
```

```{r}
fit_with_education <- lm(correct_count ~ assigned_lyrics + education, dt)
cov_with_education <- vcovHC(fit_with_education, type = 'HC')
robust.se_with_education <- sqrt(diag(cov_with_education))
```

```{r, results='asis'}
stargazer(fit_with_education,
          se=list(robust.se_with_education), 
          dep.var.labels=c("correct answer count"),
          covariate.labels=c("assigned lyrics","some high school", "high school completed","some college",
                             "vocational", "associate", "bachelor", "master", "doctorate"),
          keep.stat="n")
```


```{r, results='asis'}
fit_with_age <- lm(correct_count ~ assigned_lyrics + age, dt)
cov_with_age <- vcovHC(fit_with_age, type = 'HC')
robust.se_with_age <- sqrt(diag(cov_with_age))
```

```{r, results='asis'}
stargazer(fit_with_age,
          se=list(robust.se_with_age),
          dep.var.labels=c("correct answer count"),
          covariate.labels=c("assigned lyrics","ages 18-24", "ages 25-34","ages 35-44",
                             "ages 45-54", "ages 55-64", "ages 65-74"),
          keep.stat="n")
```

## Regression with elapsed time as outcome

```{r}
fit_time <- lm(time ~ assigned_lyrics, dt)
cov_time <- vcovHC(fit_time, type = 'HC')
robust.se_time <- sqrt(diag(cov_time))
```

With covariates
```{r}
fit_time_with_covariates <- lm(time ~ assigned_lyrics + gender + native_english + own_dog + is_turk, dt)
cov_time_with_covariates <- vcovHC(fit_time_with_covariates, type = 'HC')
robust.se_time_with_covariates <- sqrt(diag(cov_time_with_covariates))
```

```{r, results='asis'}
stargazer(fit_time, fit_time_with_covariates,
          se=list(robust.se_time, robust.se_time_with_covariates),
          dep.var.labels=c("time to complete (seconds)"),
          covariate.labels=c("assigned lyrics","female", "native english speaker","owns dog",
                             "mechanical turk"),
          keep.stat="n",type='text')
```


## Power Calculation

```{r}
# Calculating number of subjects needed for 80% power (BASED ON TIME AS THE OUTCOME)

cohens_d <- function(x, y) {
    lx <- length(x)- 1
    ly <- length(y)- 1
    md  <- abs(mean(x) - mean(y))        ## mean difference (numerator)
    csd <- lx * var(x) + ly * var(y)
    csd <- csd/(lx + ly)
    csd <- sqrt(csd)                     ## common sd computation
    
    cd  <- md/csd                        ## cohen's d
}

(effect_size_time <- cohens_d(dt[assigned_lyrics==1, time], dt[assigned_lyrics==0, time]))

pwr.t.test(power = 0.8, d = effect_size_time, sig.level = 0.05, type = "two.sample")
```



```{r}
# Calculating what power we got for our experiment

(effect_size_correct_count <- cohens_d(dt[assigned_lyrics==1, correct_count], dt[assigned_lyrics==0, correct_count]))

pwr.t2n.test(n1 = 74, n2 = 67, d = effect_size_correct_count, sig.level = 0.05)
```
```{r}
compliance_check=dt[, .N, by = 'heard_lyrics,assigned_lyrics']

alpha=sum(compliance_check$N[compliance_check$heard_lyrics=='Rocket Man' & compliance_check$assigned_lyrics==1],na.rm=TRUE)/sum(compliance_check$N[compliance_check$assigned_lyrics==1])
print(alpha)
ITT= -0.032
CACE=ITT/alpha #85% one-sided compliance
CACE
```



```{r}
dt$heard_lyrics = factor(dt$heard_lyrics, levels=c(levels(dt$heard_lyrics), "Didn't Hear"))
dt$heard_lyrics[is.na(dt$heard_lyrics)]="Didn't Hear"
dt$heard_lyrics=ifelse(dt$heard_lyrics=='Rocket Man' & dt$assigned_lyrics==1 ,1,0)
summary(dt) #re-assign heard_lyrics such that it serves as contact rate for those treated
```

```{r}
m1 <- ivreg(correct_count ~ heard_lyrics|assigned_lyrics , data = dt)
summary(m1)
```

```{r}
m2 <- ivreg(time ~ heard_lyrics|assigned_lyrics , data = dt)
summary(m2)
```

