---
title: "turk_results"
author: "Gurdit Chahal, Adam Letcher, Carlos Castro, Noah Randolph"
date: "8/7/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(stargazer)
```

## Load Data

```{r load}
dt_raw <- fread('musicdata.8.8.2018.csv')

head(dt_raw)
```

## Clean Up Columns

```{r}
dt <- dt_raw[, .(hear_song = as.integer(as.character(factor(Check1, levels = c('A', 'B'),
                                                            labels = c(1, 0)))), 
                 piano_playing = as.integer(as.character(factor(Check2, 
                                                                levels = c('A', 'B'), 
                                                                labels = c(1, 0)))),
                 q1 = as.factor(Q1), 
                 q2 = as.factor(Q2), 
                 q3 = as.factor(Q3),
                 q4 = as.factor(Q4),
                 q5 = as.factor(Q5),
                 age = factor(Q6, levels = c('A', 'B', 'C', 'D', 'E',
                                             'F', 'G', 'H', 'I', 'J'),
                              labels = c('<12', '12-17', '18-24', '25-34', '35-44',
                                         '45-54', '55-64', '65-74', '>75', 'decline')),
                 gender = factor(Q7, levels = c('A', 'B', 'C', 'D'), 
                                 labels = c('male', 'female', 'other', 'decline')),
                 own_dog = as.integer(as.character(factor(Q8, levels = c('A', 'B'), 
                                                          labels = c(1, 0)))),
                 education = factor(Q9, levels = c('A', 'B', 'C', 'D', 'E', 
                                                   'F', 'G', 'H', 'I', 'J'), 
                                    labels = c('none', '8th grade', 'some high school',
                                               'high school completed', 'some college', 
                                               'vocational', 'associates', 'bachelors', 
                                               'masters', 'doctorate')),
                 occupation = Q10, 
                 native_english = as.integer(as.character(factor(Q11, 
                                                                 levels = c('A', 'B'), 
                                                                 labels = c(1, 0)))), 
                 heard_lyrics = factor(Q13, levels = c('A', 'B', 'C', 'D', 'E', 'F'),
                                                               labels = c('I\'m a barbie girl', 
                                                                          'Rocket Man', 
                                                                          'Don\'t stop believing',
                                                                          'Hakuna Matata',
                                                                          'Lyrics but not sure',
                                                                          'No lyrics')),
                 is_turk = as.integer(as.character(factor(isTurk, 
                                                          levels = c('true', 'null'),
                                                          labels = c(1, 0)))),
                 time = time * -1, 
                 correct_count = correctCount, 
                 assigned_lyrics = as.integer(as.character(factor(lyrics, levels = c('true', 'false'),
                                                            labels = c(1, 0)))))]
```


## EDA

```{r}
summary(dt)
```


Roughly 50/50 split for treatment vs. control:
```{r}
dt[, .N, by = 'assigned_lyrics']
```


Most people recognized the song regardless of being assigned lyrics:
```{r}
dt[, .N, by = 'heard_lyrics,assigned_lyrics']
```


Turkers took roughly 40% less time to complete the survey than non-turkers:
```{r}
dt[, mean(time), by = 'is_turk']

dt[ , t.test(time ~ is_turk)]
```


No significant difference in time taken based on treatment vs. control assignment:
```{r}
dt[, mean(time), by = 'assigned_lyrics']

dt[ , t.test(time ~ assigned_lyrics)]
```


## Covariate Balance Check

```{r}
assignment_by_age <- table(dt$assigned_lyrics, dt$age)
barplot(assignment_by_age, main = 'Treatment Assignment by Age',
        xlab = "Age Range", col = c('darkblue', 'red'),
        legend = c('no lyrics', 'lyrics'))

# dt[, .N, keyby = 'age,assigned_lyrics']
```


```{r}
dt[ , chisq.test(assigned_lyrics, age, simulate.p.value = TRUE)]
dt[ , chisq.test(assigned_lyrics, education, simulate.p.value = TRUE)]
dt[ , t.test(native_english ~ assigned_lyrics)]
dt[ , t.test(is_turk ~ assigned_lyrics)]
```

## Regression


No significant difference in scores between treatment and control groups:
```{r}
fit_all <- lm(correct_count ~ assigned_lyrics, dt)
summary(fit_all)
```


The only significant difference found is that Turkers scored roughly 0.90 out of 5 lower on average:
```{r}
fit_all_with_covariates <- lm(correct_count ~ assigned_lyrics + age + education + is_turk, dt)
summary(fit_all_with_covariates)
```



```{r}
fit_turk_only <- lm(correct_count ~ assigned_lyrics, dt[is_turk == 1])
summary(fit_turk_only)
```



```{r}
fit_no_turks <- lm(correct_count ~ assigned_lyrics, dt[is_turk == 0])
summary(fit_no_turks)
```



```{r}
dt <- dt[, correct_per_second := correct_count/time]

fit_per_time <- lm(correct_per_second ~ assigned_lyrics, dt)
summary(fit_per_time)
```

